I would like to extend my sincere gratitude and appreciation to everyone who contributed to the successful completion of my internship and the preparation of this report.\mynewline

Firstly, my profound thanks to \textbf{Pr. El Akkaoui Zineb}, my internal mentor, whose continuous guidance, constructive feedback, and unwavering support greatly enhanced my internship experience. His expertise and mentorship have been invaluable, significantly shaping my professional growth.

I am equally grateful to \textbf{Mr. Rguig Saad} and \textbf{Mr. Boukhalf Ayoub}, whose insightful advice, patience, and willingness to share their extensive knowledge have enriched my learning experience. Collaborating closely with them has profoundly influenced my understanding of core concepts and helped refine my professional skillset.

Special thanks are also due to \textbf{Mr. Farini Youness} and \textbf{Ms. Ramdani Fatima Zahra}, Software Engineers in the team, whose generous support, valuable suggestions, and continuous patience contributed significantly to the success of my internship.

My sincere appreciation goes to \textbf{Mr. Hassan El Majidi} for his dedicated oversight of the internship program, ensuring a smooth and well-organized experience.

Furthermore, I extend my gratitude to the jury members, \textbf{Pr. El Ghazi Hamid} and \textbf{Pr. Soussi Khalid}, for their valuable time, insightful evaluations, and constructive feedback during the assessment of my internship report and presentation.

Finally, I would like to acknowledge the teaching and administrative staff at the National Institute of Posts and Telecommunications for their commitment to delivering high-quality education and their continual support throughout my academic journey.\mynewline

To all those mentioned above, and to anyone else who contributed to this meaningful experience, I sincerely thank you.