\fancyhead[R]{\textsc{General Introduction}}

In today's fast-paced and continuously evolving digital landscape, organizations worldwide increasingly rely on technological advancements to enhance efficiency, improve services, and maintain a competitive edge. Within this context, artificial intelligence (AI) and digital transformation have emerged as critical drivers of innovation, particularly within sectors characterized by complexity, such as government services, legal operations, and enterprise application development.\mynewline

Recognizing these evolving needs, my internship project at Boston Consulting Group - X Delivery (BCG X) focused on developing an intelligent contract management platform leveraging Agentic AI technologies. This project aimed to address inefficiencies in traditional legal contract management processes by automating and optimizing drafting, reviewing, and compliance monitoring. The goal was to significantly enhance operational efficiency, reduce processing times, and improve compliance accuracy, ultimately transforming legal operations into agile and scalable processes.\mynewline

This report systematically explores the lifecycle of this ambitious project through four detailed chapters:

\begin{itemize}
  \item {The First chapter} introduces the general context, presenting the host organization (BCG and BCG X), clearly outlining the project's scope, objectives, and the agile methodologies employed to ensure effective project management.
  \item {The Second chapter} provides a technical foundation, beginning with a comparative analysis of existing contract management solutions, justification for adopting an Agentic AI-driven approach, and a thorough specification of both functional and non-functional requirements.
  \item {The Third chapter} elaborates on the detailed system architecture and software design, presenting critical aspects such as AI integration via LangChain and LangGraph, customized implementation of Tiptap for legal document editing, and comprehensive UML diagrams illustrating the system's structural and behavioral characteristics.
  \item {The Fourth chapter} details the practical implementation and rigorous validation phases, thoroughly justifying technology selections, describing key platform functionalities, and validating system alignment with established functional and non-functional specifications.
\end{itemize}